Multimodal Information Extraction of Supermarket Leaflets

### 2025-02-25 paper/main.tex
Updates on paper

\subsection{Motivation}
When one thinks of a paper-heavy country, Germany is likely to come to mind. The country's affinity for printed materials is deeply ingrained in its culture, with activities such as browsing through supermarket leaflets serving as a familiar ritual for many individuals. These leaflets have long been an essential medium for consumers to plan their purchases, discover special offers, and compare prices.
The rapid advancement of digital technology is transforming consumer behavior. While some individuals still find browsing through physical leaflets a nostalgic and even relaxing experience, younger generations are increasingly turning to digital alternatives for their shopping needs. The modern shopper expects convenience, efficiency, and instant access to information, yet the digital transformation of supermarket leaflets in Germany lags significantly behind, even despite the existence of applications that centralize digital versions of these leaflets. The majority of these applications' digital leaflets are plain documents, failing to leverage the full potential of interactivity, searchability, and intelligent recommendation systems.

Furthermore, while price comparison websites and applications have become commonplace for electronics, fashion, and travel, the grocery sector remains an overlooked frontier. Consumers are often left navigating multiple supermarket websites or manually cross-referencing prices to find the best deals—a tedious and inefficient process. A comprehensive digital ecosystem that integrates grocery price comparisons, personalized discounts, and AI-driven shopping assistants could bridge this gap and act as a workaround, offering an enhanced, data-driven shopping experience and a tool that allows consumers to create a dynamic shopping list, track price trends over time, and receive real-time updates on the best deals.

@@

To enable advanced applications such as the abovementioned, one has to tackle different challenges, such as:
\begin{enumerate}
    \item Detecting and separating deals $p$ from the leaflet $L$.
    \item Extracting structured information from the detected deals.
    \item Normalizing the extracted information to ensure consistency and comparability.
    \item Validating the extracted information to ensure accuracy.
\end{enumerate}

@@

To enhance usability, an \emph{interactive application} is developed that allows consumers to browse, filter, and compare deals across multiple supermarket chains. It provides essential search, tracking, and comparison features for improved deal discovery.

@@

\indent{\textbf{Deal Detection}.}
There are no direct approaches for detecting deals, including product image, price, name and more, in supermarket leaflets. However, the detection of specific elements in documents, or more generally, the detection of objects in images, is a widely researched area. When it comes to just the actual detection of these elements without understanding the semantic meaning, models such as YOLO or Faster R-CNN prove to be effective. These models are able to recognize objects in images and mark them with bounding boxes and further classify them. But because there is no direct research on the detection of deals in supermarket leaflets, the research has to be done in this area.

@@

Leaflets exhibit extreme variability in design elements that impede automated parsing. The spatial heterogeneity, thus the non-standardized arrangements of product images, prices, and promotions across retailers, is a primary concern. The layout of leaflets can vary significantly, with product images, prices, and promotional text appearing in diverse configurations. Additionally, typography challenges, such as superscripted decimals, struck-through original prices, and font inconsistencies between deals and regular text, further complicate the extraction process. Overlapping elements, where text is occluded by product images or graphical overlays, violate the assumptions of Optical Character Recognition (OCR) systems, which assume planar text.

@@

\subsection{Dataset}
An approach to obtaining deal data would be direct web scraping from supermarket websites, as these days they present their deals digitally in a structured way. However, this method is highly error-prone and difficult to generalize due to the distinct and frequently changing layouts of different supermarket websites. Additionally, many retailers do not provide direct, easily scrappable structured deal data. Instead, an alternative source has been identified. Websites that aggregate and upload full promotional leaflets from various German supermarkets on a weekly basis. These leaflets provide a more standardized input format and can be systematically downloaded using an automated script.

The collected dataset consists of approximately 13,000 images from a diverse range of supermarket chains, including well-known retailers such as Penny, Aldi, and Kaufland, as well as less conventional ones like Metro. The primary focus remains on supermarkets that sell groceries and drugstore products, as these are the most relevant for the intended applications. Each leaflet page contains multiple distinct offers, which must be individually detected. This is achieved through object detection techniques, which can either utilize bounding boxes or instance segmentation. While bounding box detection provides a straightforward way to localize deals, it often struggles with overlapping offers, leading to incorrect classifications. Instance segmentation is therefore the preferred approach, as it allows for more precise extraction of deal regions without interference from neighboring offers. Deals in the dataset are categorized into four main classes:

@@

@@

To extract these entities, one aims to learn a function $f(\cdot)$ that maps an input image $I$ to the desired outputs:
\begin{equation}
    f: I \to \mathcal{Y},
\end{equation}
where $ I $ is the deal image, and $ \mathcal{Y} $ represents the extracted entities.

@@

\subsubsection{Traditional and Hybrid Approaches for Supermarket Leaflet Information Extraction}  
Information extraction from supermarket leaflets has traditionally been approached through a pipeline of sequential sub-tasks, each addressed by specialized systems. These methods, while extensively studied and methodologically diverse, are typically divided into three main stages: text detection, text recognition, and key-value pair extraction. Although effective in certain scenarios, these approaches suffer from inherent limitations, including computational overhead, error propagation, and suboptimal performance on edge cases. Recent advancements in large language models (LLMs) have led to the development of hybrid OCR-LLM architectures, which combine the precision of optical character recognition (OCR) with the contextual reasoning capabilities of LLMs. Below, we formalize these approaches and discuss their strengths and limitations.

@@

To use the recognized texts for information extraction, the final stage involves parsing the textual entities into structured outputs. This is typically achieved through rule-based systems or sequence-to-sequence models that generate key-value pairs from the recognized text. The output is a set of structured entities $ \{y_i\}_{i=1}^{N} $, where each $ y_i $ represents a specific entity (e.g., product name, price, unit).

@@

\indent{\textbf{Large Vision-Language Models (LVLMs)}.} In the realm of upscaling language models into LLMs, computer vision utilizes this trend to process multimodal data. LVLMs like Llama 3.2 Vision \cite{touvron2023} scale this framework by integrating pretrained vision encoders with large language models (LLMs). These architectures utilize \emph{cross-modal projection}, which aligns visual features with the LLM's embedding space, and \emph{multimodal decoding}, which attends to both visual tokens and textual prompts. The LVLM's strength lies in zero-shot reasoning and leveraging pretrained knowledge for structured output generation.

@@

\begin{table}[h!]
    \centering
    \caption{Leaflet-IE Dataset}
    \label{tab:ie_dataset}
    \begin{tabular}{lc}
    \toprule
    Entity           & Sample Size \\
    \midrule
    \code{image\_id}        & 372  \\
    \code{brand}            & 357  \\
    \code{product\_name}    & 370  \\
    \code{original\_price}  & 286  \\
    \code{deal\_price}      & 372  \\
    \code{weight}           & 369  \\
    \bottomrule
    \end{tabular}
    \end{table}

@@

Even though the Leaflet-IE dataset is relatively small, the reader will be able to see that the dataset is sufficient to evaluate the performance of different IE appraoches as well as to train an competitive end-to-end model. However, as the reader may notice, the dataset is solely focused on single product deals at this point and explicitly does not include

@@

The experiments aim to identify the most effective methodology for extracting structured information from supermarket leaflets by evaluating three candidate approaches: (1) Hybrid OCR + LLM pipelines, (2) end-to-end Vision-Encoder-Decoder models, and (3) Large Vision-Language Models (LVLMs). The evaluation is structured into four sequential phases to systematically assess performance and scalability.

@@

The software stack includegraphics Python with PyTorch\footnote{\href{https://pytorch.org/}{https://pytorch.org/}} as the primary deep learning framework, HuggingFace Transformers \footnote{\href{https://huggingface.co/transformers/}{https://huggingface.co/transformers/}}
for leveraging pre-trained models, ollama \footnote{\href{https://ollama.com/}{https://ollama.com/}}
and lmstudio \footnote{\href{https://lmstudio.ai/}{https://lmstudio.ai/}} for large language models and large vision-language models, and OpenCV \footnote{\href{https://opencv.org/}{https://opencv.org/}} for image preprocessing and data augmentation, as well as various other libraries for data pre-and post-processing, visualization, data management and monitoring \footnote{The codebase is available at \href{https://github.com/ilyii/leaflets}{https://github.com/ilyii/leaflets}}.

@@

Given that language-specific OCR errors are common, the evaluation was conducted at different levels of normalization to improve comparability. The text normalization included the following layers:
\begin{itemize}
    \item \textbf{Level 1:} Text stripping and string conversion.
    \item \textbf{Level 2:} Lowercasing and basic replacements.
    \item \textbf{Level 3:} Use-case specific replacements.
    \item \textbf{Level 4:} Punctuation and whitespace removal.
\end{itemize}
Each level includes the normalization steps of the previous levels. Therefore, the normalization procedure can be thought of as a gradual alignment of the OCR output to the ground truth to investigate the OCR model's robustness to different normalization levels. The reader is referred to \secref{app:ocr_normalization} for a detailed description of the normalization procedure.

@@

In addition to evaluating the OCR capabilities, the performance of OCR models was assessed in conjunction with large language models (LLMs). The primary objectives were to determine the most effective OCR-LLM combination for information extraction and to evaluate the impact of different OCR models on the LLM's performance.

@@

To avoid confusion with the normalization used in the OCR experiment, the OCR results were kept raw, as normalization may remove valuable information. The LLMs are expected to handle such inconsistencies and errors in the input. Instead, here the entity values were evaluated in both raw form and with a normalization applied for the comparability between the LLM prediction and the ground truth value . The normalization procedure includes usual character replacements and filtering based on linguistic artifacts commonly encountered in OCR errors. The specific normalization procedure can be found in \secref{app:ocr_llm_normalization}.
\paragraph{Results:}
The entity-averaged accuracies and Levenshtein distances for the raw OCR output are depicted in Figures \ref{fig:eval_ocr_llm_accuracies_avg} and \ref{fig:eval_ocr_llm_levdist_avg}, respectively.

@@

\indent{\textbf{Results}.} The training and validation losses of Donut during fine-tuning are depicted in \figref{fig:donut_loss}. The training loss decreases rapidly, while the validation loss remains high, indicating overfitting. The overfitting is likely due to the limited number of leaflet layouts in the training data, which restricts the model's ability to generalize to unseen layouts. This issue is visually less pronounced, as the text is relatively consistent across leaflets, but textually, the model struggles to generalize due to the diverse language and layout variations.

@@

This section presents a comparative evaluation of a hybrid OCR+LLM pipeline against end-to-end models, specifically Donut and Large Vision-Language Models (LVLMs), for information extraction (IE) from supermarket leaflets. The assessment focuses on model performance using the best OCR+LLM configuration and two end-to-end approaches.

\subsubsection{Experimental Setup}

The evaluation framework was designed to compare the performance of three distinct model categories: OCR+LLM pipelines, end-to-end Vision Encoder-Decoder models, and large vision-language models (LVLMs). For the OCR+LLM approach, DocTR served as the OCR engine, paired with Qwen 2.5-7B and LLaMA 3.1-8B as the large language models, selected for their comparable performance. The Donut model, an end-to-end Vision Encoder-Decoder architecture optimized for document understanding, was included to assess its capabilities in handling structured document data. Additionally, MiniCPM-V \cite{yao2024} and LLaMA 3.2-Vision \cite{touvron2023} were chosen as representative LVLMs to evaluate their multimodal reasoning abilities.

The evaluation was conducted on the Leaflet-IE validation subset, as Donut had already been trained on the training subset, ensuring a fair comparison across models. Performance was measured using two key metrics: (1) \textbf{Accuracy}, defined as the percentage of correctly extracted entity values, and (2) \textbf{Levenshtein Distance}, which quantifies the edit distance between predicted and ground truth values at the entity level. To maintain consistency, the same normalization approach employed in the OCR+LLM evaluation was applied uniformly to both model predictions and ground truth values. This setup ensured a rigorous and standardized comparison of model performance across the selected metrics.

@@

\indent{\textbf{Dicussion.}} The evaluation highlights distinct strengths and limitations across the tested models. LVLMs emerged as the most effective for information extraction (IE) tasks, particularly when spatial and visual context is critical. However, their superior performance comes at the cost of significantly higher computational requirements, making them less practical for resource-constrained environments. Donut offers a compelling trade-off between accuracy and efficiency, demonstrating strong performance despite limited training resources. With further optimization, Donut has the potential to surpass LVLMs for this specific task, though its generalization ability remains narrower compared to LVLMs, which excel across a broader range of tasks.

@@

Beyond static deal browsing, the application also incorporates an upload feature that enables users to submit entire supermarket leaflets for processing. When a leaflet is uploaded, the system applies the full processing pipeline, from deal detection using YOLO to information extraction. The processed leaflet can then be browsed interactively, displaying detected deals with their segmentation masks overlaid on the original pages. This feature provides direct insights into the model’s performance, allowing users to verify the accuracy of detected promotions and extracted information. The efficiency of the application benefits from YOLO’s lightweight architecture, ensuring that leaflet processing remains fast and responsive. After a short processing time, users can navigate through detected deals and inspect the segmentation masks applied to the leaflet images. Clicking on an individual deal reveals extracted details such as the product name, price, and other metadata. The combination of automated deal extraction and interactive visualization makes the web application a practical tool for structured deal exploration and comparison.

\section{Conclusion}
\label{sec:conclusion}
    \subsection{Summary}
    This work presents a comprehensive approach to the digitalization and structuring of supermarket leaflet information. The proposed modular pipeline encompasses deal detection and information extraction, transforming raw leaflet data into structured, actionable insights. The deal detection module leverages advanced YOLO-based models to accurately identify and segment deals within leaflets, while the information extraction module employs state-of-the-art OCR, LLM, and end-to-end models to extract and normalize deal attributes. The developed interactive application, backed by a robust database, allows users to browse, filter, and compare deals across multiple supermarket chains, providing a proof of concept for practical applications. Additionally, the research contributes two datasets: one for deal detection as instance segmentation and another for image-based information extraction, facilitating further research in this domain.

@@

    Firstly, enhancing the performance and runtime of the deal detection module is crucial. This involves optimizing the existing YOLO-based model and exploring alternative architectures that may offer better accuracy and efficiency.

    Secondly, the information extraction (IE) component can be significantly improved by building a larger dataset specifically for training the Donut model. Given the promising results achieved with Donut, expanding the dataset and fine-tuning the model further could yield competitive results in extracting structured information from supermarket leaflets.

    Additionally, several new branches of research and development can be pursued. These include the deal specification and product image extraction to build a comprehensive database, brand and product name normalization for database mapping, and time series analysis for price trend prediction. On the application side, scalability, frontend improvements, and additional features such as a recommendation engine and automatic weekly deal extraction can enhance user experience and system robustness.

>>>>

\subsection{Motivation}
When one thinks of a paper-heavy country, Germany is likely to come to mind. The country's affinity for printed materials is deeply ingrained in its culture, with activities such as browsing through supermarket leaflets serving as a familiar ritual for many individuals. These leaflets have long been an essential medium for consumers to plan their purchases, discover special offers, and compare prices.
The rapid advancement of digital technology is transforming consumer behavior. While some individuals still find browsing through physical leaflets a nostalgic and even relaxing experience, younger generations are increasingly turning to digital alternatives for their shopping needs. The modern shopper expects convenience, efficiency, and instant access to information, yet the digital transformation of supermarket leaflets in Germany lags significantly behind, even despite the existence of applications that centralize digital versions of these leaflets. The majority of these digital leaflets are plain documents, failing to leverage the full potential of interactivity, searchability and intelligent recommendation systems.

Furthermore, while price comparison websites and applications have become commonplace for electronics, fashion and travel, the grocery sector remains an overlooked frontier. Consumers are often left navigating multiple supermarket websites or manually cross-referencing prices to find the best deals. This is often a tedious and inefficient process. A comprehensive digital ecosystem that integrates grocery price comparisons, personalized discounts and AI-driven shopping assistants could bridge this gap and act as a workaround, offering an enhanced, data-driven shopping experience and a tool that allows consumers to create a dynamic shopping list, track price trends over time, and receive real-time updates on the best deals.

@@

To enable advanced applications such as the abovementioned, one has to tackle different challenges, such as:
\begin{enumerate}
    \item Gathering a diverse set of supermarket leaflets from various retailers.
    \item Detecting and separating deals $p$ from the leaflet $L$.
    \item Extracting structured information from the detected deals.
    \item Normalizing the extracted information to ensure consistency and comparability.
    \item Validating the extracted information to ensure accuracy.
    \item Storing the extracted information in a structured format for efficient querying and comparison.
    \item Developing an interactive application for browsing and comparing deals across multiple supermarket chains.
\end{enumerate}

@@

To enhance usability, an \emph{interactive application} is developed that allows consumers to browse, filter, and compare deals across multiple supermarket chains. In addition, a feature allows an entire leaflet to be uploaded and the entire pipeline to be run in order to examine the deals in detail. This application serves as a proof of concept for the proposed system and demonstrates its practical utility.

@@

\indent{\textbf{Deal Detection}.}
There are no direct approaches for detecting deals, including product image, price, name and more, in supermarket leaflets. However, the detection of specific elements in documents, or more generally, the detection of objects in images, is a widely researched area. When it comes to just the actual detection of these elements without understanding the semantic meaning, models such as YOLO or Faster R-CNN prove to be effective. These models are able to recognize objects in images and mark them with bounding boxes and further classify them. 
% TODO: Add more advanced methods for object/instant segmentation

@@

Leaflets exhibit extreme variability in design elements that impede automated parsing. The spatial heterogeneity, thus the non-standardized arrangements of product images, prices, and promotions across retailers, is a primary concern. The layout of leaflets can vary significantly, with product images, prices, and promotional text appearing in diverse configurations. Additionally, typography challenges, such as superscripted decimals, struck-through original prices, and font inconsistencies between deals and regular text, further complicate the extraction process. Overlapping elements, where text is occluded by product images or graphical overlays, violate the assumptions of OCR systems, which assume planar text.

@@

\subsection{Dataset}
An approach to obtaining deal data would be direct web scraping from supermarket websites, as these days they present their deals digitally in a structured way. However, this method is highly error-prone and difficult to generalize due to the distinct and frequently changing layouts of different supermarket websites. Additionally, many retailers do not provide direct, easily scrappable structured deal data. Instead, an alternative source has been identified. Websites that aggregate and upload full promotional leaflets from various German supermarkets on a weekly basis. These leaflets provide a more standardized input format and can be systematically downloaded using an automated script.
% TODO: add url source

The collected dataset consists of approximately 13,000 images from a diverse range of supermarket chains, including well-known retailers such as Penny, Aldi, and Kaufland, as well as less conventional ones like Metro. The primary focus remains on supermarkets that sell groceries and drugstore products, as these are the most relevant for the intended applications. Each leaflet page contains multiple distinct deals, which must be individually detected. This is achieved through object detection techniques, which can either utilize bounding boxes or instance segmentation. While bounding box detection provides a straightforward way to localize deals, it often struggles with overlapping deals, which can lead to inaccurate information extraction and misclassification of deals later on. Instance segmentation is therefore the preferred approach, as it allows for more precise extraction of deal regions without interference from neighboring deals. Deal Objects in the dataset are categorized into four main classes:

@@

% TODO: Referenz auf untenstehende Figures.

@@

To extract these entities, the target is to learn a function $f(\cdot)$ that maps an input image $I$ to the desired outputs:
\begin{equation}
    f: I \to \mathcal{Y},
\end{equation}
where $ I $ is the deal image, and $ \mathcal{Y} $ represents the extracted entities.

@@

\subsubsection{Traditional and Hybrid Approaches for Supermarket Leaflet Information Extraction}  
Information extraction from supermarket leaflets has traditionally been approached through a pipeline of sequential sub-tasks, each addressed by specialized systems. These methods, while extensively studied and methodologically diverse, are typically divided into three main stages: text detection, text recognition, and key-value pair extraction. Although effective in certain scenarios, these approaches suffer from inherent limitations, including computational overhead, error propagation, and suboptimal performance on edge cases. Recent advancements in LLMs have led to the development of hybrid OCR-LLM architectures, which combine the precision of OCR with the contextual reasoning capabilities of LLMs. Below, we formalize these approaches and discuss their strengths and limitations.

@@

To use the recognized texts for information extraction, the final stage involves parsing the textual entities into structured outputs. This is typically achieved through rule-based systems or sequence-to-sequence models that generate key-value pairs from the recognized text. The output is a set of structured entities $ \{y_i\}_{i=1}^{N} $, where each $ y_i $ represents one of the desired attributes.

@@

\indent{\textbf{Large Vision-Language Models (LVLMs)}.} In the realm of upscaling language models into LLMs, computer vision utilizes this trend to process multimodal data. LVLMs like Llama 3.2 Vision \cite{touvron2023} scale this framework by integrating pretrained vision encoders with LLMs. These architectures utilize \emph{cross-modal projection}, which aligns visual features with the LLM's embedding space, and \emph{multimodal decoding}, which attends to both visual tokens and textual prompts. The LVLM's strength lies in zero-shot reasoning and leveraging pretrained knowledge for structured output generation.

@@

\begin{table}[h!]
    \centering
    \caption{Leaflet-IE Dataset with a sum of 372 annotated deals.}
    \label{tab:ie_dataset}
    \begin{tabular}{lc}
    \toprule
    Entity           & Sample Size \\
    \midrule
    \code{brand}            & 357  \\
    \code{product\_name}    & 370  \\
    \code{original\_price}  & 286  \\
    \code{deal\_price}      & 372  \\
    \code{unit}           & 369  \\
    \bottomrule
    \end{tabular}
\end{table}

@@

Even though the Leaflet-IE dataset is relatively small, the reader will be able to see that the dataset is sufficient to evaluate the performance of different IE appraoches as well as to train an competitive end-to-end model. However, as the reader may notice, the dataset is solely focused on single product deals at this point and explicitly does not include
% TODO: Missing Text (ILYI)

@@

% TODO: Remove cause of ambiguity? (ILYI)
% The experiments aim to identify the most effective methodology for extracting structured information from supermarket leaflets by evaluating three candidate approaches: (1) Hybrid OCR + LLM pipelines, (2) end-to-end Vision-Encoder-Decoder models, and (3) LVLMs. The evaluation is structured into four sequential phases to systematically assess performance and scalability.

@@

The software stack includegraphics Python with PyTorch\footnote{\href{https://pytorch.org/}{https://pytorch.org/}} as the primary deep learning framework, HuggingFace Transformers \footnote{\href{https://huggingface.co/transformers/}{https://huggingface.co/transformers/}}
for leveraging pre-trained models, ollama \footnote{\href{https://ollama.com/}{https://ollama.com/}}
and lmstudio \footnote{\href{https://lmstudio.ai/}{https://lmstudio.ai/}} for LVLMs, and OpenCV \footnote{\href{https://opencv.org/}{https://opencv.org/}} for image preprocessing and data augmentation, as well as various other libraries for data pre-and post-processing, visualization, data management and monitoring \footnote{The codebase is available at \href{https://github.com/ilyii/leaflets}{https://github.com/ilyii/leaflets}}.
% TODO: Remove this section or move it to the appendix or introduction because it is also relevant for deal detection chapter? (ILYI)

@@

Given that language-specific OCR errors are common, the evaluation was conducted at different levels of normalization to improve comparability. The text normalization included the following layers:
\begin{itemize}
    \item \textbf{Level 1:} Text stripping and string conversion.
    \item \textbf{Level 2:} Lowercasing and basic replacements.
    \item \textbf{Level 3:} Use-case specific replacements.
    \item \textbf{Level 4:} Punctuation and whitespace removal.
\end{itemize}
Each level includes the normalization steps of the previous levels. Therefore, the normalization procedure can be thought of as a gradual alignment of the OCR output to the ground truth to investigate the OCR model's robustness to different normalization levels. A detailed description of the normalization procedure can be found in \secref{app:ocr_normalization}.

@@

In addition to evaluating the OCR capabilities, the performance of OCR models was assessed in conjunction with LLMs. The primary objectives were to determine the most effective OCR-LLM combination for information extraction and to evaluate the impact of different OCR models on the LLM's performance.

@@

To avoid confusion with the normalization used in the OCR experiment, the OCR results were kept raw, as normalization may remove valuable information. The LLMs are expected to handle such inconsistencies and errors in the input. Instead, here the entity values were evaluated in both raw form and with a normalization applied for the comparability between the LLM prediction and the ground truth value. The normalization procedure includes usual character replacements and filtering based on linguistic artifacts commonly encountered in OCR errors. The specific normalization procedure can be found in \secref{app:ocr_llm_normalization}.
\paragraph{Results:}
The entity-averaged accuracies and Levenshtein distances for the raw OCR output are depicted in Figures \ref{fig:eval_ocr_llm_accuracies_avg} and \ref{fig:eval_ocr_llm_levdist_avg}, respectively.

@@

\indent{\textbf{Results}.} The training and validation losses of Donut during fine-tuning are depicted in \figref{fig:donut_loss}. The training loss decreases rapidly, while the validation loss remains high, indicating overfitting. The overfitting is likely due to the limited number of deal layouts in the training data, which restricts the model's ability to generalize to unseen layouts. This issue is visually less pronounced, as the text is relatively consistent across deals, but textually, the model struggles to generalize due to the diverse language and layout variations. Another problem is that the model is not pretrained on the German language, which may further hinder its performance.

@@

This section presents a comparative evaluation of a hybrid OCR+LLM pipeline against end-to-end models, specifically Donut and LVLMs, for IE from supermarket deals. The assessment focuses on model performance using the best OCR+LLM configuration and two end-to-end approaches.

\subsubsection{Experimental Setup}
% TODO: Remove \subsection{Comparison of Hybrid OCR+LLM, Donut, and LVLM} because it is the same as the following? (ILYI)
The evaluation framework was designed to compare the performance of three distinct model categories: OCR+LLM pipelines, end-to-end Vision Encoder-Decoder models, and LVLMs. For the OCR+LLM approach, DocTR served as the OCR engine, paired with Qwen 2.5-7B and LLaMA 3.1-8B as the large language models, selected for their comparable performance. The Donut model, an end-to-end Vision Encoder-Decoder architecture optimized for document understanding, was included to assess its capabilities in handling structured document data. Additionally, MiniCPM-V \cite{yao2024} and LLaMA 3.2-Vision \cite{touvron2023} were chosen as representative LVLMs to evaluate their multimodal reasoning abilities.

The evaluation was conducted on the Leaflet-IE validation subset, ensuring a fair comparison across the models. Donut had already been fine-tuned on the training subset. The same metrics, accuracy and Levenshtein distance, were employed to assess model performance. To maintain consistency, the same normalization approach used in the OCR+LLM evaluation was applied uniformly to both model predictions and ground truth values. This setup ensured a rigorous and standardized comparison of model performance across the selected metrics.

@@

\indent{\textbf{Dicussion.}} The evaluation highlights distinct strengths and limitations across the tested models. LVLMs emerged as the most effective for IE tasks, particularly when spatial and visual context is critical. However, their superior performance comes at the cost of significantly higher computational requirements, making them less practical for resource-constrained environments. Donut offers a compelling trade-off between accuracy and efficiency, demonstrating strong performance despite limited training resources. With further optimization, Donut has the potential to surpass LVLMs for this specific task, though its generalization ability remains narrower compared to LVLMs, which excel across a broader range of tasks.

@@

Beyond static deal browsing, the application also incorporates an upload feature that enables users to submit entire supermarket leaflets for processing. When a leaflet is uploaded, the system applies the full processing pipeline, from deal detection using YOLO to information extraction. The processed leaflet can then be browsed interactively, displaying detected deals with their segmentation masks overlaid on the original pages. This feature provides direct insights into the models performance, allowing users to verify the accuracy of detected promotions and extracted information. The efficiency of the application benefits from  lightweight architecture from YOLO, ensuring that leaflet processing remains fast and responsive. After a short processing time, users can navigate through detected deals and inspect the segmentation masks applied to the leaflet images. Clicking on an individual deal reveals extracted details such as the product name, price, and other metadata. The combination of automated deal extraction and interactive visualization makes the web application a practical tool for structured deal exploration and comparison.

\section{Conclusion}
\label{sec:conclusion}
    \subsection{Summary}
    This work presents a comprehensive approach to the digitalization and structuring of supermarket leaflet deals. The proposed modular pipeline encompasses deal detection and information extraction, transforming raw leaflet data into structured data. The deal detection module leverages lightweight and efficient YOLO-based models to accurately identify and segment deals within leaflets, while the information extraction module employs state-of-the-art OCR, LLM, and end-to-end models to extract and normalize deal attributes. The developed interactive application, backed by a robust database, allows users to browse, filter, and compare deals across multiple supermarket chains, providing a proof of concept for practical applications. Additionally, the research contributes two datasets: one for deal detection as instance segmentation and another for image-based information extraction, facilitating further research in this domain.

@@

    Firstly, enhancing the performance and runtime of the deal detection module is crucial. This involves optimizing the existing YOLO-based model and exploring alternative architectures that may offer better accuracy and efficiency. Also, the size of the dataset can be increased by including more leaflets from different supermarkets, which would improve the model's generalization capabilities.

    Secondly, the IE component can be significantly improved by building a larger dataset specifically for training the Donut model. Given the promising results achieved with Donut, expanding the dataset and fine-tuning the model further could yield competitive results in extracting structured information from supermarket leaflets.

    Additionally, several new branches of research and development can be pursued. These include the deal specification and product image extraction to build a comprehensive database, brand and product name normalization for database mapping, and time series analysis for price trend prediction. On the application side, scalability, frontend improvements, and additional features such as a recommendation engine and automatic weekly deal extraction can enhance user experience and system robustness. There are numerous possibilities for future work and the project serves as a foundation for further exploration in the field of supermarket deal extraction based on leaflets.
